\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-10 stlc-linkTran-typing.tex
tweaks

We use \lsti{STLCBool} as an example. \lsti{STLCBool} extends
\lsti{STLC} with boolean values (\lsti{tm_true} and \lsti{tm_false})
and if-then-else expressions.
The left column of the table below shows initial code excerpted from
this family.
Each cell in the last column defines a linkage transformer~$h_i$
inductively constructed from the linkage transformers $h_0$, ..., $h_{i-1}$.
The goal is to eventually construct a linkage transformer $h_n$ representing
the entire family \lsti{STLCBool}.

Of note is the two grayed rows. They are constructing a linkage~$h_\beta$
containing the case handlers for \lsti{subst}.
This linkage $h_\beta$ is then appended as a nested linkage to $h_3$.

@@

% Please add the following required packages to your document preamble:
% \usepackage[table,xcdraw]{xcolor}
% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
\begin{centered}
\small
\renewcommand*{\arraystretch}{1.25}
\begin{tabular}{|l|l|l|}
\hline
\rowcolor[HTML]{FFFC9E} 
surface-syntax program & $i$      & $\goodInh{\cdot}{h_i}{\lsig_i}{\lsig_i'}$             \\ \hline
\lsti!Family STLCBool!   & 0        & $\InhId$                                             \\ \cline{2-3} 
\lsti!FInductive tm += !       & 1        & $\InhOv{h_0}{\wcode{\wsig_{\texttt{tm}}'}}$                      \\ \cline{2-3} 
\codecomment{existing constructors}   & 2        & $\InhOv{h_1}{\Wsup{\wsig_{\texttt{tm}}'}{\top}{\bot}}$           \\ \cline{2-3} 
\lsti!| tm_true |!\ \;\dadada    & 3        & $\InhExt{h_2}{\Wsup{\wsig_{\texttt{tm}}'}{\top}{\bot}}$          \\ \cline{2-3} 
\rowcolor[HTML]{CDCDCD} 
\lsti!FRecursion subst!\ \;\dadada\ \;\lsti!+=! & $\alpha$ & $\InhId$ \\ \cline{2-3} 
\rowcolor[HTML]{CDCDCD} 
\lsti!  Case tm_true := !\dadada. & $\beta$  & $\InhExt{h_\alpha}{...}$ \\ \cline{2-3} 
\rowcolor[HTML]{FFFFFF} 
\lsti!End subst.!              & 4        & $\InhNest{h_3}{h_\beta}$
  %with $\uparrow^s_3$
  \\ \cline{2-3} 
                          & 5        & $\InhOv{h_4}{\lambda t. \Wrec{\wsig_{\texttt{tm}}'}{t}{"substCases"}}$ \\ \cline{2-3} 
\lsti!FInductive ty += !\dadada. & 6        & ...                                                  \\ \cline{2-3} 
\codecomment{Inherit "env"}   & 7        & $\InhInh{h_6}$
  %with $\uparrow^s_6$
  \\ \cline{2-3} 
\codecomment{Inherit "empty"}   & 8        & $\InhInh{h_7}$
  \\ \cline{2-3} 
\dadada   & \dadada & \dadada
  \\ \hline
\end{tabular}
\end{centered}

>>>>

We use \lsti{STLCBool} as an example. \lsti{STLCBool} extends
\lsti{STLC} with boolean values (\lsti{tm_true} and \lsti{tm_false})
and if-then-else expressions.
The left column of the table below shows initial code excerpted from
this family.
Each cell in the last column defines a linkage transformer~$h_i$
inductively constructed from the linkage transformers $h_0$, ..., $h_{i-1}$
using one of the introduction forms.
The goal is to eventually construct a linkage transformer $h_n$ representing
the entire family \lsti{STLCBool}.

Of note is the two grayed rows. They are constructing a linkage transformer~$h_\beta$
containing the case handlers for \lsti{subst}.
This $h_\beta$ is then appended to $h_3$ as a nested linkage transformer.

@@

% Please add the following required packages to your document preamble:
% \usepackage[table,xcdraw]{xcolor}
% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
\begin{centered}
\small
\renewcommand*{\arraystretch}{1.25}
\begin{tabular}{|l|l|l|}
\hline
\rowcolor[HTML]{FFFC9E} 
surface-syntax program & $i$      & $\goodInh{\cdot}{h_i}{\lsig_i}{\lsig_i'}$             \\ \hline
\lsti!Family STLCBool!   & 0        & $\InhId$                                             \\ \cline{2-3} 
\lsti!FInductive tm += !       & 1        & $\InhOv{h_0}{\wcode{\wsig_{\texttt{tm}}'}}$                      \\ \cline{2-3} 
\codecomment{existing constructors}   & 2        & $\InhOv{h_1}{\Wsup{\wsig_{\texttt{tm}}'}{\top}{\bot}}$           \\ \cline{2-3} 
\lsti!| tm_true |!\ \;\dadada    & 3        & $\InhExt{h_2}{\Wsup{\wsig_{\texttt{tm}}'}{\top}{\bot}}$          \\ \cline{2-3} 
\rowcolor[HTML]{CDCDCD} 
\lsti!FRecursion subst!\ \;\dadada\ \;\lsti!+=! & $\alpha$ & $\InhId$ \\ \cline{2-3} 
\rowcolor[HTML]{CDCDCD} 
\lsti!  Case tm_true := !\dadada. \lsti! Case !\dadada & $\beta$  & $\InhExt{h_\alpha}{...}$ \\ \cline{2-3} 
\rowcolor[HTML]{FFFFFF} 
\lsti!End subst.!              & 4        & $\InhNest{h_3}{h_\beta}$
  %with $\uparrow^s_3$
  \\ \cline{2-3} 
                          & 5        & $\InhOv{h_4}{\lambda t. \Wrec{\wsig_{\texttt{tm}}'}{t}{"substCases"}}$ \\ \cline{2-3} 
\lsti!FInductive ty += !\dadada. & 6        & ...                                                  \\ \cline{2-3} 
\codecomment{Inherit "env"}   & 7        & $\InhInh{h_6}$
  %with $\uparrow^s_6$
  \\ \cline{2-3} 
\codecomment{Inherit "empty"}   & 8        & $\InhInh{h_7}$
  \\ \cline{2-3} 
\dadada   & \dadada & \dadada
  \\ \hline
\end{tabular}
\end{centered}
